MSB104_assignment1

### 2023-10-10 MSB104_assignment1.qmd
Update 10.10.23

```{r}
# Since Germany contains many regions, we have deceided to present them in two new values.
# DEz1North and DEz2SOUTH are the two values where we have devided Germany in South and North. 
DEz1NORTH <- c("DE30", "DE40", "DE50", "DE60", "DE80", "DE91", "DE92", "DE93", "DE94", "DEA1", "DEA2", "DEA3", "DEA4", "DEA5", "DEE0", "DEF0", "DEG0") 
DEz2SOUTH <- c("DE11", "DE12", "DE13", "DE14", "DE21", "DE22", "DE23", "DE24", "DE25", "DE26", "DE27", "DE71", "DE72", "DE73", "DEB1", "DEB2", "DEB3", "DEC0", "DED2", "DED4", "DED5")
DE <- c(DEz1NORTH, DEz2SOUTH)
```

```{r}
# First step is to place the location of the figure caption and name it.
# Secondly, we filter GDP_DE_nuts2 to contain integer starting from 3 and ending with 4. Moreover, in this dataset we only contain vales larger or equal to 0, but less than 50.
# Thirdly, we represent the data in GPD_DE_nuts2 by mapping them in a plot using ggplot, where the x-axis represents year and y-axis represents GPD_per_capita. Furthermore the colour is determined by id_nuts2.
# Fourthly, we exclude the geom_smooth and instead use geom_line since this gives a accurate description of our data from Germany.
#| cap-location: bottom
#| fig-cap: "GDP per year."
GDP_DE_nuts2 |>
  filter(
    id_nuts2 %in% DEz1NORTH
  ) |> 
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_DE, 
    colour = id_nuts2)
    ) +
  #geom_smooth(se = FALSE, snap = 0.9)
  geom_line()
```

```{r}
GDP_DE_nuts2 |>
  filter(
    id_nuts2 %in% DEz2SOUTH
  ) |> 
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_DE, 
    colour = id_nuts2)
    ) +
  #geom_smooth(se = FALSE, snap = 0.9)
  geom_line()
```

@@

```{r}
# First step is to place the location of the figure caption and name it.
# Secondly, we filter GDP_FI_nuts2 to contain integer starting from 3 and ending with 4. Moreover, in this dataset we only contain vales larger or equal to 0, but less than 50.
# Thirdly, we represent the data in GPD_FI_nuts2 by mapping them in a plot using ggplot, where the x-axis represents year and y-axis represents GPD_per_capita. Furthermore the colour is determined by id_nuts2.
# Fourthly, we exclude the geom_smooth and instead use geom_line since this gives a accurate description of our data from Finland
#| cap-location: bottom
#| fig-cap: "GDP per year."
GDP_FI_nuts2 |>
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_FI, 
    colour = id_nuts2)
    ) +
  #geom_smooth(se = FALSE, snap = 0.9)
  geom_line()
```

@@

```{r}
# First step is to place the location of the figure caption and name it.
# Secondly, we filter GDP_RO_nuts2 to contain integer starting from 3 and ending with 4. Moreover, in this dataset we only contain vales larger or equal to 0, but less than 50.
# Thirdly, we represent the data in GPD_RO_nuts2 by mapping them in a plot using ggplot, where the x-axis represents year and y-axis represents GPD_per_capita. Furthermore the colour is determined by id_nuts2.
# Fourthly, we exclude the geom_smooth and instead use geom_line since this gives a accurate description of our data from Romania
#| cap-location: bottom
#| fig-cap: "GDP per year."
GDP_RO_nuts2 |>
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_RO, 
    colour = id_nuts2)
    ) +
  #geom_smooth(se = FALSE, snap = 0.9)
  geom_line()
```

@@

```{r}
Gini_stat_DE_nuts2 <- merged_temp %>%
  filter(id_nuts2 %in% DE) |> 
  group_by(Year) |> 
  summarise(
    min_Gini_each_year = min(gini_n2),
    max_Gini_each_year = max(gini_n2),
    median_Gini_each_year = median(gini_n2),
    mean_Gini_each_year = mean(gini_n2),
    sd_Gini_each_year = sd(gini_n2),
    var_Gini_each_year = sd_Gini_each_year^2
  )
```

@@

```{r}
Gini_stat_FI_nuts2 <- merged_temp %>%
  filter(id_nuts2 %in% FI) |> 
  group_by(Year) |> 
  summarise(
    min_Gini_each_year = min(gini_n2),
    max_Gini_each_year = max(gini_n2),
    median_Gini_each_year = median(gini_n2),
    mean_Gini_each_year = mean(gini_n2),
    sd_Gini_each_year = sd(gini_n2),
    var_Gini_each_year = sd_Gini_each_year^2
  )
```

@@

```{r}
Gini_stat_RO_nuts2 <- merged_temp %>%
  filter(id_nuts2 %in% RO) |> 
  group_by(Year) |> 
  summarise(
    min_Gini_each_year = min(gini_n2),
    max_Gini_each_year = max(gini_n2),
    median_Gini_each_year = median(gini_n2),
    mean_Gini_each_year = mean(gini_n2),
    sd_Gini_each_year = sd(gini_n2),
    var_Gini_each_year = sd_Gini_each_year^2
  )
```

>>>>

```{r}
# Since Germany contains many regions, we have deceided to present them in two new values.
# DEz1North and DEz2SOUTH are the two values where we have devided Germany in South and North. 
# Created a combined value consisting of the Northern and Southern part of Germany.
DEz1NORTH <- c("DE30", "DE40", "DE50", "DE60", "DE80", "DE91", "DE92", "DE93", "DE94", "DEA1", "DEA2", "DEA3", "DEA4", "DEA5", "DEE0", "DEF0", "DEG0") 
DEz2SOUTH <- c("DE11", "DE12", "DE13", "DE14", "DE21", "DE22", "DE23", "DE24", "DE25", "DE26", "DE27", "DE71", "DE72", "DE73", "DEB1", "DEB2", "DEB3", "DEC0", "DED2", "DED4", "DED5")
DE <- c(DEz1NORTH, DEz2SOUTH)
```

```{r}
# First step is to place the location of the figure caption and name it.
# Secondly, we filter GDP_DE_nuts2 to contain integer starting from 3 and ending with 4. Moreover, in this dataset we only contain vales larger or equal to 0, but less than 50.
# Thirdly, we represent the data in GPD_DE_nuts2 by mapping them in a plot using ggplot, where the x-axis represents year and y-axis represents GPD_per_capita. Furthermore the colour is determined by id_nuts2.
# Fourthly, we use geom_line since this gives a accurate description of our data from Germany.
#| cap-location: bottom
#| fig-cap: "GDP per year."
GDP_DE_nuts2 |>
  filter(
    id_nuts2 %in% DEz1NORTH
  ) |> 
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_DE, 
    colour = id_nuts2)
    ) +
  geom_line()
```

```{r}
# Duplicating the same steps for Southern Germany as for the Northern part. 
GDP_DE_nuts2 |>
  filter(
    id_nuts2 %in% DEz2SOUTH
  ) |> 
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_DE, 
    colour = id_nuts2)
    ) +
  geom_line()
```

@@

```{r}
# First step is to place the location of the figure caption and name it.
# Secondly, we filter GDP_FI_nuts2 to contain integer starting from 3 and ending with 4. Moreover, in this dataset we only contain vales larger or equal to 0, but less than 50.
# Thirdly, we represent the data in GPD_FI_nuts2 by mapping them in a plot using ggplot, where the x-axis represents year and y-axis represents GPD_per_capita. Furthermore the colour is determined by id_nuts2.
# Fourthly, we use geom_line since this gives a accurate description of our data from Finland
#| cap-location: bottom
#| fig-cap: "GDP per year."
GDP_FI_nuts2 |>
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_FI, 
    colour = id_nuts2)
    ) +
  geom_line()
```

@@

```{r}
# First step is to place the location of the figure caption and name it.
# Secondly, we filter GDP_RO_nuts2 to contain integer starting from 3 and ending with 4. Moreover, in this dataset we only contain vales larger or equal to 0, but less than 50.
# Thirdly, we represent the data in GPD_RO_nuts2 by mapping them in a plot using ggplot, where the x-axis represents year and y-axis represents GPD_per_capita. Furthermore the colour is determined by id_nuts2.
# Fourthly, we use geom_line since this gives a accurate description of our data from Romania
#| cap-location: bottom
#| fig-cap: "GDP per year."
GDP_RO_nuts2 |>
  ggplot(mapping = aes(
    x = Year, 
    y = GDP_per_capita_nuts2_RO, 
    colour = id_nuts2)
    ) +
  geom_line()
```

@@

```{r}
# Firstly, we create a new dataset called Gini_stat_DE_nuts2. 
# Secondly, we filter the data to include only rows where the id_nuts2 variable is in the DE group. 
# Thirdyly, after filtering, the data is grouped by the Year variable. This means that subsequent calculations will be performed separately for each year.
# Lastly, we use summarise to calculates summary statistics for the gini_n2 variable within each group (each year). 
Gini_stat_DE_nuts2 <- merged_temp %>%
  filter(id_nuts2 %in% DE) |> 
  group_by(Year) |> 
  summarise(
    min = min(gini_n2),
    max = max(gini_n2),
    median = median(gini_n2),
    mean = mean(gini_n2),
    sd = sd(gini_n2),
    var = sd^2
  )
```

```{r}
# Firstly, we add a table caption. 
# Secondly, we remove grouping and then we add a new group containing year, min, max, median, mean, sd and var. 
# Thirdly, we use kable to create a create nicely formatted table.
#| tbl-cap: Descriptive statistics based on Gini coeffisient from NUTS2 level in Germany
Gini_stat_DE_nuts2 |> 
  ungroup() |> 
  select(Year, min, max, median, mean, sd, var) %>%
  kable(digits = 5)
```

@@

```{r}
Gini_stat_FI_nuts2 <- merged_temp %>%
  filter(id_nuts2 %in% FI) |> 
  group_by(Year) |> 
  summarise(
    min = min(gini_n2),
    max = max(gini_n2),
    median = median(gini_n2),
    mean = mean(gini_n2),
    sd = sd(gini_n2),
    var = sd^2
  )
```

```{r}
#| tbl-cap: Descriptive statistics based on Gini coeffisient from NUTS2 level in Finland
Gini_stat_FI_nuts2 |> 
  ungroup() |> 
  select(Year, min, max, median, mean, sd, var) %>%
  kable(digits = 5)
```

@@

```{r}
Gini_stat_RO_nuts2 <- merged_temp %>%
  filter(id_nuts2 %in% RO) |> 
  group_by(Year) |> 
  summarise(
    min = min(gini_n2),
    max = max(gini_n2),
    median = median(gini_n2),
    mean = mean(gini_n2),
    sd = sd(gini_n2),
    var = sd^2
  )
```

```{r}
#| tbl-cap: Descriptive statistics based on Gini coeffisient from NUTS2 level in Romania
Gini_stat_RO_nuts2 |> 
  ungroup() |> 
  select(Year, min, max, median, mean, sd, var) %>%
  kable(digits = 5)
```
